On the combination of Set Functions and Failures

### 2013-05-21 docs/src/manual.tex

There are a few minor restrictions on Curry programs
when they are processed with \CYS:
\begin{itemize}
\item
\index{singleton variables}\index{variables!singleton}
\emph{Singleton pattern variables}, i.e., variables that occur only once
in a rule, should be denoted as an anonymous variable \ccode{_},
otherwise the parser will print a warning since this is a
typical source of programming errors.
\item
\CYS translates all \emph{local declarations} into global functions with
additional arguments (``lambda lifting'', see Appendix~D of the
Curry language report).
Thus, in the various run-time systems, the definition of
functions with local declarations look different from
their original definition (in order to see the result
of this transformation, you can use the \cb, see
Section~\ref{sec-currybrowser}).
\item \index{tabulator stops}
Tabulator stops instead of blank spaces in source files are
interpreted as stops at columns 9, 17, 25, 33, and so on.
In general, tabulator stops should be avoided in source programs.
\item
Encapsulated search\index{encapsulated search}: In order
to allow the integration of non-deterministic computations
in programs performing I/O at the top-level, \CYS provides
the libraries \code{AllSolutions} (Section~\ref{Library:AllSolutions})
and \code{SearchTree} (Section~\ref{Library:SearchTree})
where one can defined search operators and various search strategies.
The general definition of encapsulated search of the Curry report
\cite{HanusSteiner98PLILP} is not supported.
\item Concurrent computations\index{concurrency}
based on the suspension of expressions
containing free variables are not yet supported.
\CYS supports \emph{value generators} for free variables
so that a free variable is instantiated when its value is demanded.
For instance, the initial expression
\begin{curry}
x == True where x free
\end{curry}
is non-deterministically evaluated to \code{False} and \code{True}
by instantiating \code{x} to \code{False} and \code{True}, respectively.
Thus, a computation is never suspended due to free variables.
This behavior also applies to free variables of primitive types
like integers. For instance, the initial expression
\begin{curry}
x*y=:=1 where x,y free
\end{curry}
is non-deterministically evaluated to the two solutions
\begin{curry}
{x = -1, y = -1} Success
{x = 1, y = 1} Success
\end{curry}
\item
Unification is performed without an occur check.
\item
There is currently no general connection to external constraint solvers.
\end{itemize}

>>>>

There are a few minor restrictions on Curry programs
when they are processed with \CYS:
\begin{itemize}
\item
\index{singleton variables}\index{variables!singleton}
\emph{Singleton pattern variables}, i.e., variables that occur only once
in a rule, should be denoted as an anonymous variable \ccode{_},
otherwise the parser will print a warning since this is a
typical source of programming errors.
\item
\CYS translates all \emph{local declarations} into global functions with
additional arguments (``lambda lifting'', see Appendix~D of the
Curry language report).
Thus, in the various run-time systems, the definition of
functions with local declarations look different from
their original definition (in order to see the result
of this transformation, you can use the \cb, see
Section~\ref{sec-currybrowser}).
\item \index{tabulator stops}
Tabulator stops instead of blank spaces in source files are
interpreted as stops at columns 9, 17, 25, 33, and so on.
In general, tabulator stops should be avoided in source programs.
\item
Encapsulated search\index{encapsulated search}:
The general definition of encapsulated search of the Curry report
\cite{HanusSteiner98PLILP} is not supported.
Thus, the corresponding prelude operations like
\code{try}\pindex{try},
\code{solveAll}\pindex{solveAll},
\code{once}\pindex{once},
\code{findall}\pindex{findall}, or
\code{best}\pindex{best}
are not defined in the \CYS prelude.
However, \CYS supports appropriate alternatives
to encapsulate non-deterministic computations:
\begin{description}
\item[Strong encapsulation:]
This means that all potential
non-determinism is encapsulated. Since this might
result in dependencies on the evaluation strategy
(see \cite{BrasselHanusHuch04JFLP} for a detailed discussion),
this kind of encapsulation is only available as I/O operations.
For instance, the library \code{AllSolutions}\pindex{AllSolutions}
(Section~\ref{Library:AllSolutions})
defines the operation
\begin{curry}
getAllValues :: a -> IO [a]
\end{curry}
to compute all values of a given argument expression.
There is also the library \code{SearchTree}\pindex{SearchTree}
(Section~\ref{Library:SearchTree})
which supports user-programmable search strategies
and contains some predefined strategies
like depth-first, breadth-first, iterative deepening search.
\item[Weak encapsulation:]
This means that only the non-determinism
defined inside an encapsulation operator is encapsulated.
Conceptually, these operators are offered as
\emph{set functions}\index{set functions} \cite{AntoyHanus09}
which compute the set of all results but do not encapsulate
non-determinism in the actual arguments.
See the library \code{SetFunctions}
(Section~\ref{Library:SetFunctions}) for more details.
\end{description}
\item
Concurrent computations\index{concurrency}
based on the suspension of expressions
containing free variables are not yet supported.
\CYS supports \emph{value generators} for free variables
so that a free variable is instantiated when its value is demanded.
For instance, the initial expression
\begin{curry}
x == True where x free
\end{curry}
is non-deterministically evaluated to \code{False} and \code{True}
by instantiating \code{x} to \code{False} and \code{True}, respectively.
Thus, a computation is never suspended due to free variables.
This behavior also applies to free variables of primitive types
like integers. For instance, the initial expression
\begin{curry}
x*y=:=1 where x,y free
\end{curry}
is non-deterministically evaluated to the two solutions
\begin{curry}
{x = -1, y = -1} Success
{x = 1, y = 1} Success
\end{curry}
\item
Unification is performed without an occur check.
\item
There is currently no general connection to external constraint solvers.
\end{itemize}
